Thesis Title

### 2022-03-26 chapters/thesis_outline.tex
fix mistake

bioinformatics

>>>>

\textbf{Chapter 8} showcases an effort to raise standards on the development and distribution of code for bioinformatic analysis. For this, seven recommendations are presented that help researchers implement software testing in microbial bioinformatics. We propose collaborative software testing as an opportunity to continuously engage software users, developers, and students to unify scientific work across domains. As automated software testing remains underused in scientific software, our set of recommendations not only ensures that appropriate effort can be invested in producing high quality and robust software, but also increases engagement in its sustainability.
